NodIO: a Framework and Architecture for Pool-based Evolutionary Computation

### 2016-05-04 EvoSoft16/nodio-evosoft16.tex
Keywords added when submitting
Thanks anyway @mariosky Closes #122
New new version for EvoSoft

@@

\title{NodIO: a framework and architecture for pool-based evolutionary
  computation} 
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
\alignauthor
Juan-J.~Merelo, Pedro A. Castillo, Pablo Garc\'ia-S\'anchez, Paloma de las Cuevas\\
\affaddr{Dept. of Computer Architecture and Technology
  and CITIC, University of Granada, Granada, Spain} \\
\email{(jmerelo|pacv|pablogarcia|palomacd)@ugr.es}
\alignauthor
Mario Garc\'ia-Valdez,\affaddr{ Dept. of Graduate Studies, Instituto
Tecnológico de Tijuana, Tijuana, M\'exico}\\
}

>>>>

\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\usepackage[
  pass,% keep layout unchanged 
  % showframe,% show the layout
]{geometry}

@@

\title{NodIO: a Framework and Architecture for Pool-based Evolutionary Computation} 
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{5} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
\alignauthor
Juan-J.~Merelo\\
Pedro A. Castillo\\
Pablo Garc\'ia-S\'anchez\\
Paloma de las Cuevas\\
\affaddr{Dept. of Computer Architecture and Technology
  and CITIC, University of Granada, Granada, Spain} \\
\email{(jmerelo|pacv|pablogarcia|palomacd)@ugr.es}
\alignauthor
Mario Garc\'ia-Valdez,
\affaddr{ Dept. of Graduate Studies, Instituto
Tecnológico de Tijuana, Tijuana, M\'exico}
\email{mario@tectijuana.edu.mx}\\
}
